\documentclass{article}
\usepackage{listings}
\usepackage{xcolor}

\lstset{
    language=bash,
    basicstyle=\ttfamily,
    keywordstyle=\color{blue},
    commentstyle=\color{gray},
    stringstyle=\color{red},
    frame=single,
    breaklines=true,
    postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space}
}
\begin{document}

\LARGE
    \textbf{{Software Tools and Technology\\
        -: Lab Notebook :-}}
    \vspace{0.5cm}\\
\textbf{Name} : Oindrila Chatterjee\\
\textbf{Roll No.} : 30059223022 



\newpage
\title{Git Branching, Merging, and Conflict Resolution}
\author{}
\date{}


\maketitle

\section*{Objective}
The objective of this assignment was to demonstrate proficiency in Git branching, merging, and conflict resolution. The tasks involved creating a Git repository, working with branches, pushing changes, merging branches, resolving conflicts, and deleting branches upon completion.

\section*{Steps Followed}
\begin{enumerate}
    \item \textbf{Create a new repository on GitHub}\\
    Created a new GitHub repository called \texttt{git-advanced}. The repository was initialized without any files.
    
    \item \textbf{Clone the repository to the local machine}\\
    Used the command \texttt{git clone <repository\_url>} to clone the repository locally.
    
    \item \textbf{Create a new branch "feature-1" and switch to it}\\
    Used the following command:
    \begin{lstlisting}
    git checkout -b feature-1
    \end{lstlisting}
    This command created a new branch called \texttt{feature-1} and switched to it.

    \item \textbf{Create and modify \texttt{shared.txt}}\\
    Created a new file named \texttt{shared.txt} with the following content:
    \begin{lstlisting}[language={}]
    This is a shared file.
    Line 1: Original text.
    Line 2: Original text.
    \end{lstlisting}
    Staged and committed the file:
    \begin{lstlisting}
    git add shared.txt
    git commit -m "Add shared.txt with original content"
    \end{lstlisting}

    \item \textbf{Push "feature-1" branch to GitHub}\\
    Used the command \texttt{git push origin feature-1} to push the branch to GitHub.

    \item \textbf{Create another branch "feature-2"}\\
    Switched back to the \texttt{main} branch and created another branch:
    \begin{lstlisting}
    git checkout main
    git checkout -b feature-2
    \end{lstlisting}

    \item \textbf{Checkout and modify \texttt{shared.txt} in "feature-2"}\\
    Checked out the \texttt{shared.txt} file from the \texttt{main} branch. Modified the second line in \texttt{shared.txt}:
    \begin{lstlisting}[language={}]
    Line 2: Modified text in feature-2.
    \end{lstlisting}
    Staged and committed the changes:
    \begin{lstlisting}
    git add shared.txt
    git commit -m "Modify Line 2 in feature-2"
    \end{lstlisting}

    \item \textbf{Push "feature-2" branch to GitHub}\\
    Used the command \texttt{git push origin feature-2} to push the branch.

    \item \textbf{Modify \texttt{shared.txt} in "feature-1"}\\
    Switched back to the \texttt{feature-1} branch:
    \begin{lstlisting}
    git checkout feature-1
    \end{lstlisting}
    Modified the second line in \texttt{shared.txt}:
    \begin{lstlisting}[language={}]
    Line 2: Modified text in feature-1.
    \end{lstlisting}
    Staged and committed the changes:
    \begin{lstlisting}
    git add shared.txt
    git commit -m "Modify Line 2 in feature-1"
    \end{lstlisting}

    \item \textbf{Push "feature-1" branch to GitHub}\\
    Used the command \texttt{git push origin feature-1} to push the branch.

    \item \textbf{Merge "feature-1" into the main branch}\\
    Merged \texttt{feature-1} into the \texttt{main} branch:
    \begin{lstlisting}
    git checkout main
    git merge feature-1
    \end{lstlisting}

    \item \textbf{Merge "feature-2" into the main branch (conflict)}\\
    Attempted to merge \texttt{feature-2} into the \texttt{main} branch:
    \begin{lstlisting}
    git merge feature-2
    \end{lstlisting}
    This resulted in a conflict in \texttt{shared.txt} due to the different modifications made to Line 2.

    \item \textbf{Resolve the conflict}\\
    Edited the \texttt{shared.txt} file to resolve the conflict:
    \begin{lstlisting}[language={}]
    This is a shared file.
    Line 1: Original text.
    Line 2: Merged text from both feature-1 and feature-2.
    \end{lstlisting}
    Staged and committed the resolution:
    \begin{lstlisting}
    git add shared.txt
    git commit -m "Resolve conflict between feature-1 and feature-2"
    \end{lstlisting}

    \item \textbf{Push the updated main branch to GitHub}\\
    Pushed the resolved changes to the \texttt{main} branch:
    \begin{lstlisting}
    git push origin main
    \end{lstlisting}

    \item \textbf{Delete the "feature-1" and "feature-2" branches}\\
    Deleted the branches after merging.
\end{enumerate}

\end{document}
